Weather Data Integration and Assimilation System\\

### 2020-02-09 introduction/sec_3-outline.tex
Change Bib to References

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in Chapter \ref{ch:literature}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}

>>>>

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias} etc. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides more details about how the \acrshort{wdias} is design with following the microservice architecture, and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}, and there we discussed about experiment setup of the \acrshort{wdias} and the observations. Then analyze the observations with respect to performance metrics. At the last chapter \ref{ch:conc}, it concludes and summarize the work, and further discussed about the research limitations.
